\defcitealias{PPatch21}{PPatch21}
\defcitealias{PReadme22}{PReadme22}

\section*{Related Work}
As of now, there are already numerous solutions for automating web actions on the market. 
A majority of those uses existing web browsers and offer a programmable interface for simulating user input.

\textbf{Cypress} is a \ac{E2E} Javascript testing framework containing various assertions for \ac{QA} testing of webpages.
It supports multiple web browsers and offers its own UI and toolkit for test programming and running. 
Due to its strong orientation towards testing, it does not provide much methods for data extraction and crawling.

\textbf{Selenium WebDriver} is a fairly popular tool among web UI testers, as it offers a wide variety of methods for \ac{QA} testing.
Distributed as a multilanguage library, Selenium implements a high-level interface for controlling web browsers from code.
% Aside from regular commercial web browsers, Selenium also implements interfaces for PhantomJS and HTMLUnit, both headless scriptable browsers used as a lightweight alternative to regular browsers.

\textbf{Puppeteer} is a low-level library used for web browser automation. 
Unlike Cypress and Selenium, Puppeteer supports Chrome (or Chromium) as its only backend browser as of now (\today).

The communication with the browser is implemented via WebSockets and the DevTools Protocol, a Chromium-specific set of commands.
This allows Puppeteer to exceed Selenium both in stability and performance, sporting up to $17\%$ speedup in benchmarks \citepalias{Chck21}.

\textbf{Playwright} is another low-level library multilanguage library offering programmable ways of controlling web browser.
For browser communication, Playwright uses similiar technology as Puppeteer, unlike Puppeteer, Playwright supports multiple commercial browsers (Chromium, Firefox, Webkit as of \today).

Due to differences between browsers and partial incompatibility of protocols, Playwright is distributed with patched versions of Firefox and Webkit \citepalias{PPatch21}.
Stock versions of Chromium based browsers (Google Chrome, Microsoft Edge) are supported. \citepalias{PReadme22}

\emptyline

All the aforementioned examples however require programming, which can mean a significant barrier to entry for beginners.