\chapter{Design}

This chapter describes decisions made while designing parts of the project. 
It contains separate sections for all three parts of the project, i.e. \textit{the format}, \textit{the interpreter} and \textit{the editor}.

Design decisions made here should reflect the requirements mentioned in the previous chapter.
These decisions also directly influence the implementation of the project described further.

\section{Workflow definition format}

As both the \textit{interpreter} and \textit{the editor} work directly with the files containing the workflow definitions, the first part of the project to be designed is the workflow definition format itself.

The workflow definition files should contain all the information needed to describe an arbitrary web-related workflow. 
The files in this format should also be parsable, human- and machine-readable and provide a simple yet powerful way of programming the web automations.

\subsection{Programming logic}

As the workflow definitions are computer programs of sorts, the first design decision needs to be what programming concepts will the file format implement.
To retain the steep learning curve and user-friendliness, this programming ``language'' also should not be too complicated.

The popularity of other automation tools shows that one of the simplest forms of programming is \textit{declarative programming}.
Defining the desired results rather than describing the complete control flow allows users to program the automations without being exposed to complicated programming principles.

Inspired by logic programming languages such as \textit{Prolog}, the workflow definition should contain a set of \textit{conditions} describing a possible state of the environment, connected to their respective \textit{reactions}, describing a sequence of actions to be carried out in case the condition applies.

% The similarity with \textit{Prolog} can be seen here, with the \textit{conditions} corresponding to \textit{Prolog's} fact \textit{heads} and \textit{reactions} to their respective \textit{bodies}.

\subsection{Conditions}

As stated before, the workflow definition format should allow the user to specify web environment-related conditions for running the automation steps.

Such conditions can be e.g. the browser visiting a certain \texttt{url}, the current page containing certain \texttt{selectors} or the current browser session having \texttt{cookies} set to specific values.

Moreover, the format should allow the user to combine the base conditions using \textit{boolean operators} to create more comprehensible and compact syntax.

Following through with the \textit{Prolog} comparison, the workflow definition could look something like this:

\begin{minipage}{0.95\linewidth}
\begin{verbatim}
    % X is denoting the current state of the browser
    nextState(X) :- url(X, "https://jindrich.bar"),
                        % action to be 
                        % executed on 
                        % https://jindrich.bar
    
    nextState(X) :- selector(X, "button"),
                        % action to be 
                        % executed if the current 
                        % page contains a button
    
    nextState(X) :- cookies(X, "key", "value"),
                        % action to be 
                        % executed if the current 
                        % browser session has the
                        % `key` cookie for the  
                        % page set to `value`
    
    nextState(X) :- url(X, "https://example.org"),
                    selector(X, "input"),
                        % action to be 
                        % executed in case of both
                        % conditions matching 
                        % (boolean AND example)
\end{verbatim}
\end{minipage}

\subsection{Reactions}

The workflow definition format should also allow the user to specify the actions to be carried out when the respective condition matches.

Those can be e.g. \texttt{click}, \texttt{goto}, \texttt{scrapeData} and similar. 
The actions should be chainable, allowing the user to specify a set of actions to be executed sequentially, without additional condition matching between those.

Completing the \textit{Prolog-inspired} example from the previous section, the complete workflow definition would look like this:

\begin{minipage}{0.95\linewidth}
\begin{verbatim}
    % X is denoting the current state of the browser

    nextState(X) :- url(X, "https://jindrich.bar"),
                    goto(X, "https://example.org").
    
    nextState(X) :- selector(X, "button"),
                    click(X, "button").
    
    nextState(X) :- cookies(X, "key", "value"),
                        % action to be 
                        % executed if the current 
                        % browser session has the
                        % `key` cookie for the  
                        % page set to `value`
    
    nextState(X) :- url(X, "https://example.org"),
                    selector(X, "input"),
                    fill(X, "input", "hello").
\end{verbatim}
\end{minipage}

\subsection{Serialization}

\defcitealias{GTrends22}{GTrends22}
\defcitealias{Medium21}{Medium21}

Finally, the workflow definition needs to be physically stored in a file. 
As it would be rather counterproductive to develop a custom file format for storing the conditions and reactions, the workflow definitions might be stored using a host meta-format.

Based on the hierarchical nature of both \textit{condition-action} pairs and possibly recursive nature of the \textit{conditions} themselves, it would be only logical to store the definitions using a hierarchical data format like \textit{JSON}, \textit{XML} or \textit{YAML}.

Comparing these formats, \textit{JSON} comes out as the most popular \citepalias{GTrends22} and most space-saving \citepalias{Medium21}. 
While the advanced features of \textit{XML} are invaluable when working with complex structured data, it is perhaps too complicated for storing well-defined workflow definitions.

With YAML taking first place, JSON is also a runner-up in human readability.
While improving the file legibility, the indentation oriented nature of YAML makes it very prone to input errors - this problem is absent in JSON because of its bracket-oriented grammar.

For the reasons mentioned, the workflow definition format will be built upon JSON - a host format providing a simple, human-readable serialization for structured schema of the definitions.

\subsubsection{}